### 2019-09-07 manuscript/manuscript.tex
ms updates

Finally, we observed that in the \gc{longest study}  we   %run evolve-and-resequence 
analyzed \parencite{Barghi2019-qy}, some genome-wide temporal covariances
\gc{become} negative at future timepoints (see the first two rows in
Figure \ref{fig:figure-1} A). \gc{This shows that alleles that were on
average going up initially are no going down in frequency, i.e. that
the average direction of selection experienced by alleles has
flipped. This must reflect either a change in the environment or the
genetic background, due to changing epistatic relationships among
alleles or  recombination breaking up selective alleles.}
\gc{Such reversals of selective dynamics could be occuring at other time-points but} the
signal of a change in the direction of selection \gc{at particular
  loci} may be washed out when we calculate our  genome-wide \gc{average} temporal
covariances. To address this limitation, we
calculated \gc{the distribution of the} temporal covariances over
100kb genomic windows \gc{(Figure \ref{fig:figure-3}, pooling
across all replicates see Supplementary Figure \ref{suppfig:barghi-offset-replicate-panels} for individuals replicates).}
\gc{The}
covariance of each tile is noisy, \gc{due to sampling and genetic
  drift, shown in }. \gc{The neutral distribution of the covariance is
  complicated due to} linkage
disequilibria (which can occur over long physical distances in E\&R and
selection studies, \cite{Nuzhdin2013-gf,Baldwin-Brown2014-cl}). 
\gc{Thus} we have developed a permutation-based procedure that constructs a null
distribution by randomly flipping the signs of the    %of the
                                %genome-wide covariances as they would
                                %look if only neutral genetic drift was acting. We do this 
allele frequency changes per-genomic window. \gc{This destroys}  %%  GC bit about 1,000 times seems more like figgure caption or methods
the systematic covariances created by linked selection but creates a sampling
distribution of the covariances spuriously created by neutral genetic
drift while preserve the complex dependencies
between adjacent loci created by linkage disequilibrium (see Supplementary
Material Section \ref{supp:empirical-null} for more details on this approach).
This empirical neutral null distribution is conservative in the sense that the
variances of the covariances are wider than expected under drift
alone \gc{as they include the effect of selection on the alele
  frequency change within a time-interval, just not between
  time-intervals.} We see, Figure \ref{fig:figure-3} A and B, that
windowed temporal covariances between close timepoints are skewed positive (a
heavy right tail), while between more distant timepoints these windowed
temporal covariances tend to shift to become more negative (a heavy
left tail).
We quantified the degree to which the left and right
tails \gc{are inflated compared to the null distribution as a function
  of time}, and see excesses in both tails in Figure
\ref{fig:figure-3} C. This finding is also
robust to sign-permuting allele frequency changes on a chromosome-level, the
longest extent that gametic linkage disequilibria can extend {\bf ????} (Supplementary
Figure \ref{suppfig:barghi-tailprobs-seqid}).  \gc{We} see a striking
pattern that \gc{the windowed} covariances not only decay towards zero, but in fact become
negative through time, consistent with \gc{many} regions in the genome having had a
reversed fitness effect at later timepoints.

@@

%since
%drift also acts to inflate the magnitude of allele frequency change. By
f%lipping the sign at the block-level, we

%we can  % (mean \gc{SNP} perwindow 4,606, median 4,830)
%analyze the genome-wide distribution of tile covariances for changes through
t%ime. We would like to compare the distribution of these tile covariances to a
%neutral expectation, but using a theoretic neutral null distribution would be
%inappropriate given complex dependencies across the genome due to linkage
%disequilibria (which can occur over long physical distances in E\&R and
%selection studies, \cite{Nuzhdin2013-gf,Baldwin-Brown2014-cl}).

>>>>

Finally, we observed that in the \gc{longest study}  we 
analyzed \parencite{Barghi2019-qy}, some genome-wide temporal covariances
\gc{become} negative at future timepoints (see the first two rows in
Figure \ref{fig:figure-1} A). \gc{This shows that alleles that were on
average going up initially are no going down in frequency, i.e. that
the average direction of selection experienced by alleles has
flipped. This must reflect either a change in the environment or the
genetic background, due to changing epistatic relationships among
alleles or  recombination breaking up selective alleles.}
\gc{Such reversals of selective dynamics could be occuring at other time-points but} the
signal of a change in the direction of selection \gc{at particular
  loci} may be washed out when we calculate our  genome-wide \gc{average} temporal
covariances. To address this limitation, we
calculated \gc{the distribution of the} temporal covariances over
100kb genomic windows \gc{(Figure \ref{fig:figure-3}, pooling
across all replicates see Supplementary Figure \ref{suppfig:barghi-offset-replicate-panels} for individuals replicates).}
\gc{The}
covariance of each tile is noisy, \gc{due to sampling and genetic
  drift, shown in }. \gc{The neutral distribution of the covariance is
  complicated due to} linkage
disequilibria (which can occur over long physical distances in E\&R and
selection studies, \cite{Nuzhdin2013-gf,Baldwin-Brown2014-cl}). 
\gc{Thus} we have developed a permutation-based procedure that constructs a null
distribution by randomly flipping the signs of the    %of the
                                %genome-wide covariances as they would
                                %look if only neutral genetic drift was acting. We do this 
allele frequency changes per-genomic window. \gc{This destroys}  %%  GC bit about 1,000 times seems more like figgure caption or methods
the systematic covariances created by linked selection but creates a sampling
distribution of the covariances spuriously created by neutral genetic
drift while preserve the complex dependencies
between adjacent loci created by linkage disequilibrium (see Supplementary
Material Section \ref{supp:empirical-null} for more details on this approach).
This empirical neutral null distribution is conservative in the sense that the
variances of the covariances are wider than expected under drift
alone \gc{as they include the effect of selection on the allele
  frequency change within a time-interval, just not between
  time-intervals.} We see, Figure \ref{fig:figure-3} A and B, that
windowed temporal covariances between close timepoints are skewed positive (a
heavy right tail), while between more distant timepoints these windowed
temporal covariances tend to shift to become more negative (a heavy
left tail).
We quantified the degree to which the left and right
tails \gc{are inflated compared to the null distribution as a function
  of time}, and see excesses in both tails in Figure
\ref{fig:figure-3} C. This finding is also
robust to sign-permuting allele frequency changes on a chromosome-level, the
longest extent that gametic linkage disequilibria can extend {\bf ????} (Supplementary
Figure \ref{suppfig:barghi-tailprobs-seqid}).  \gc{We} see a striking
pattern that \gc{the windowed} covariances not only decay towards zero, but in fact become
negative through time, consistent with \gc{many} regions in the genome having had a
reversed fitness effect at later timepoints.

@@

\section{Discussion}

Since the seminal theoretic model of \textcite{Maynard_Smith1974-lc}
demonstrating that diversity is reduced at linked neutral variation as a
advantageous polymorphism sweeps fixation, over four decades of theoretical and
empirical research has enriched our understanding of linked selection. This
work has led to the discovery of selected genes from genomic signals of
hitchhiking \parencite{Nair2003-tw,Voight2006-rn}, found genome-wide signals of
linked selection
\parencite{Aguade1989-jx,Begun1992-ey,Cutter2010-gi,Andersen2012-bj,Cutter2003-tl}
leading to the development of recurrent hitchhiking \parencite{Stephan1992-jc}
and background selection \parencite{Charlesworth1993-gb} models that attempt
explain this pattern. Since, much attention has focused on quantifying the
impact of background selection \parencite{McVicker2009-ax} and developing
theoretic machinery \parencite{Coop2012-cd} to differentiate the regional
reductions in diversity into those caused by full and partial sweeps, and those
caused by background selection \parencite{Elyashiv2016-vt}. However, as other
theoretic models of soft sweeps from standing variation emerged
\parencite{Hermisson2005-hs,Pennings2006-lj}, attention shifted towards
detecting other modes of linked selection \parencite{Pritchard2010-tk}, a more
difficult endeavor \parencite{Przeworski2005-bg} met with new coalescent models
\parencite{Berg2015-xj} and machine learning methods
\parencite{Schrider2017-yx}. An undervalued theoretic approach to understanding
the genome-wide effects of selection on standing variation, e.g. selection on
an infinitesimal polygenic trait, stems from an early quantitative genetic
model of linked selection \parencite{Robertson1961-ho} and its later
developments \parencite{Santiago1995-hx,Santiago1998-bs}. Implicit in these
models is that autocovariance between allele frequency change is created when
there is heritable fitness variation in the population, a signal that can be
readily detected from temporal genomic data \parencite{Buffalo2019-io}. Here,
we provide the first empirical evidence of linked selection acting on standing
variation over very short timescales.

We re-analyzed three published temporal genomic datasets and detected the
genome-wide signature of linked selection acting over tens of generations.
Furthermore, we find the dynamics of temporal autocovariance are consistent
with theory; as linkage disequilibria and additive variation for fitness decay
through time, temporal covariance decays. In reanalyzing one study
\parencite{Barghi2019-qy}, we find that after sixty generations, greater than
20\% of the variation in allele frequency change is directly due to the action
linked selection. Capitalizing on replicated evolve-and-resequence study
designs, we characterized the extent to which convergent selection pressures
lead to parallel changes in allele frequency across replicate populations,
finding that the correlation in allele frequency changes varies from 0.1 (in
the \cite{Barghi2019-qy} study) to 0.36 (in the \cite{Kelly2019-dc} study).

While we must keep in mind that the studies analyzed here were all laboratory
populations and natural selection in the wild will likely differ, overall we
have found that linked selection has a remarkably strong effect for such short
study durations. Depending on how polygenic fitness variation is, such a strong
effect of linked selection may not be differentiable from genetic drift using
only single contemporary population samples. In this way, temporal data allows
us to sidestep the key problem of detecting selection from standing variation:
that the genomic footprint leaves too soft of a signature to differentiate from
a background of genetic drift. In fact we find that the temporal covariance
signal is detectable even in the most extremely difficult to detect soft sweep
case: polygenic selection on an infinitesimal trait. In our reanalysis of the
\textcite{Castro2019-uk} data, by showing the covariance signal remains even
after excluding the chromosomes containing two large-effect loci, we showed the
covariance signal we detect is indeed driven by polygenic fitness variation
(and confirm a point in the original study that tibiae length, aside from these
two large effect loci, is an infinitesimal trait).

It is worth building some intuition why temporal covariance allows us to detect
such faint signals of polygenic linked selection from temporal genomic data.
Each variant is subject to both variance in allele frequency due to drift and
two levels of sampling noise (as individuals are sampled from the population
and reads are sampled from amplified DNA), which at any locus swamps the
temporal covariance signal and creates spurious covariances. However, these
spurious covariances do not share a common sign across timepoints as the
covariances created by linked selection do; consequently, averaging across the
entire genome, the temporal signal exceeds sampling noise.

One limitation of our current work here is that none of the studies we
re-analyzed had linkage disequilibria data for the evolved populations. Our
theory of temporal autocovariance tells us that the temporal autocovariances a
neutral site experiences is determined by the product of the expected linkage
disequilibrium and additive fitness variation that persists through the
generations. This leads to a clear prediction: regions of higher linkage
disequilibrium and lower recombination should have greater temporal
autocovariance than regions with lower LD and higher recombination.
Unfortunately, we lack a high-resolution recombination map for \emph{D.
simulans} and while there are LD data for \emph{D. simulans}
\parencite{Signor2018-wg} we did not find a relationship between temporal
covariance and LD.

We believe this is driven by the idiosyncratic nature of LD in
evolve-and-resequence populations \parencite{Nuzhdin2013-gf,Kelly2019-dc}, and
that we might find such a relationship if LD data from the evolved population
were available. Unfortunately, sequencing multiple timepoints is expensive and
the low-coverage and/or pooled-sequencing approaches common in these studies
prohibit estimating linkage disequilibrium. Future studies complete with LD
data and recombination maps would allow one to disentangle the influence of
closely linked sites from more distant sites in causing temporal
autocovariance, and allow us better understand sites in high recombination
regions are free from the effects of linked selection. Furthermore, such
additional data would allow for localizing the effects of temporal covariance,
which would allow us to estimate not just the genome-wide fraction of variation
in frequency change ($G(t)$), but also the fraction of genome impacted by
linked selection, allowing us to synthesize the temporal approach with
single-timepoint studies like that of \textcite{Elyashiv2016-vt}.

%Why the variation in convergence correlations?

Thus far, the most comprehensive studies implicating linked selection in
affecting genome-wide diversity have been in \emph{Drosophila}
\parencite{Begun1992-ey,Elyashiv2016-vt,Sattath2011-dr} and
\emph{Caenorhabditis} \cite{Cutter2003-tl,Cutter2003-tl,Andersen2012-bj},
whereas the evidence for linked selection in plant and yeast species is weak
\parencite{Cutter2013-ba}. Both \emph{Drosophila} and \emph{Caenorhabditi} have
short genetic maps (or in the case of selfing \emph{C.  elegans}, small
effective recombination rates), and large effect population sizes, two factors
predicted to increase the degree to which hitchhiking impacts genome-wide
diversity \parencite{Barton2000-zg}. However, our results here show that even
with small effective population sizes (300, 450, and 45 for the
\textcite{Kelly2019-dc}, and \textcite{Castro2019-uk} studies respectively)
around and, in the case of mice, moderately-sized genetic maps (around 14
Morgans; \cite{Cox2009-hf}), we still see a fairly strong effect of linked
selection. This suggests that while these factors may govern the dynamics of
classic hitchhiking events, they could perhaps play less of a role in polygenic
linked selection. However, with only three cases here, further studies on
different taxa are needed.

Finally, in re-analyzing the \textcite{Barghi2019-qy} study, we find evidence
of linked selection dynamics more complex than expected under a model of
directional selection occurring until fitness variation is exhausted. This is
due either to a change in the environment and its consequences for the fitness
of regions in the genome, recombination breaking up selected alleles, or
epistatic interactions between loci. It is important to note that the original
study did not intentionally alter the environment in any way; this signal is
attained without intentionally seeking it out. Discerning which of these is
creating negative temporal autocovariance is a sizable challenge, requiring
sequencing each generation and LD data.

Overall, we hope this will encourage more temporal genomic studies in both
laboratory and natural populations. Understanding the dynamics of linked
selection over short timescales can help us finally unite phenotypic studies of
rapid adaptation of polygenic adaptations with a detectable genomic signature,
to address long-standing questions on linked selection, evolutionary
quantitative genetics, and the overall impact selection has on genetic
variation.

%since
%drift also acts to inflate the magnitude of allele frequency change. By
%flipping the sign at the block-level, we

%we can  % (mean \gc{SNP} perwindow 4,606, median 4,830)
%analyze the genome-wide distribution of tile covariances for changes through
%time. We would like to compare the distribution of these tile covariances to a
%neutral expectation, but using a theoretic neutral null distribution would be
%inappropriate given complex dependencies across the genome due to linkage
%disequilibria (which can occur over long physical distances in E\&R and
%selection studies, \cite{Nuzhdin2013-gf,Baldwin-Brown2014-cl}).
